\documentclass[margin,line]{res}

\usepackage[utf8]{inputenc}
\usepackage{paralist}
\usepackage{hyperref}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Frederic Portaria-Janicki, B. Ing.\vspace*{.1in}}

\begin{resume}
\section{\sc Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
4822 Saint-Andre street& {\it Mobile:}  (514) 969-9816 \\            
Montreal, Quebec, H2J 3A3 &{\it Email:} frederic@janicki.ninja\\      
\end{tabular}

%%%%%%%%%%%%% FORMATION ACADEMIQUE %%%%%%%

%%%%%%%%%%%%%% ETS Genie Electrique %%%%%%%%%

\section{\sc Education}
{\bf Electrical and Computer Engineering} \hfill {\bf 2015}\\
École de technologie supérieure (ÉTS)
Université du Québec, Montréal

%%%%%%%%%%%%%% Cegep %%%%%%%%%%%%%%%

{\bf DEC: Pure and applied science} \hfill {\bf 2010}\\
Jean-de-Brébeuf College

%%%%%%%%%%%%%%% TRAVAIL %%%%%%%%%%%

\section{\sc Professional Experience}
{\bf Samsao} \hfill {\bf 2016}\\
Mobile Developer - Software Engineering\\\\
Native Android mobile development of a solution used to configure and flash custom firmwares on an IoT embedded device in the automotive industry by using a Bluetooth Low Energy link.

{\emph Technology Stack:} Java, Android SDK, Git, Jenkins, Reactive Extensions (RxJava), Bluetooth Low Energy, Clean Architecture.

{\bf nventive} \hfill {\bf 2015}\\
Mobile Developer - Software Engineering\\\\
Multiplatform mobile development for various clients using Xamarin and C\#.
{\emph Examples of clients:} Rdio, Twitter.

{\emph Technology stack:} C\#, Xamarin, .NET 5, Android SDK, iOS, Git, Visual Studio Online.

%\begin{compactitem}
%\item Programmation orientée objet en langage C\#
%\end{compactitem}

{\bf Mobeewave} \hfill {\bf 2015}\\
Intern - Software Engineering\\\\
Developed a scalable backend application in C\# for a mobile financial application using an {\emph Agile} methodology. Designed and implemented a shared caching system. 

{\emph Technology stack:} C\#, .NET 4.5, Amazon AWS, Redis, WebApi, Git, TFS, Visual Studio Online.

%\begin{compactitem}
%\item Programmation orientée objet en langage C\#
%\end{compactitem}

{\bf iBwave} \hfill {\bf 2014}\\
Intern - Software Engineering\\\\
Removed and corrected various issues found in the current version of \emph{iBwave design} and worked on implementing next-generation features to be included in the next release.

{\emph Technology stack:} C\#, XML, .NET 4.5

%\begin{compactitem}
%\item Programmation orientée objet en langage C\#
%\end{compactitem}

{\bf Hewlett-Packard} \hfill {\bf 2012-2013}\\
Intern - Software/Hardware QA Engineering 

{\bf CGI} \hfill {\bf 2008-2012}\\
IT Consultant

%%%%%%%%%% Connaissances Particulieres %%%%%%%%

\section{\sc Skills}

{\bf Computer Science} \\
Programming languages:  Java, C, C\#, Xamarin, Android, iOS, GLSL\\
Software and design principles:  SOLID, Clean Architecture, Reactive Extension, TouchDesigner, \LaTeX \\\\
{\bf Electronics} \\
Digital Design, Hardware Design, Microcontrollers Programming.

%%%%%%%%%%%% AUTRES EXP %%%%%%%%%%%%%%

\section{\sc Additional\\ Information}
{\bf Projects}\hfill
\begin{itemize}
\item Designed and built a geodesic dome as part of a multidisciplinary project for the \emph{OpenMind 2015 Festival}. The project received a prize from the festival for it's ecological design. I also had the Technical Director role for a north american tour for the same project during summer 2016.
\item Designed and built a 500 LED wall with numerical interactive controls. Presented at various  events, including a networking event organized by Facebook.
\\\\{\emph Technology Stack:} TouchDesigner, ARM Cortex-M4, C, Serial Communication, Laser Cutting, Electronics Design.
\item Developed a VJing custom interactive solution, presented at various events.
\end{itemize}
{\bf Implication} \hfill
\begin{itemize}
\item Co-founder and technical director of the {\emph Eden Creative} technological and artistic collective.
\item Ex-Member of the video game development club {\emph Conjure} at ETS.
\item Developed a multiplayer video game prototype for the Academia 2014 competition, organized by Ubisoft Montreal. Our prototype won 2 of the 10 available prizes.
\item Attended the NorthSec 2014 computer security competition.
\item Volunteered at the Engineering Games 2012.
\end{itemize}
%%%%%%%%%%% Mentions%%%%%%%%%%%%%%%%%

%%%%%%%%%%% LOISIRS %%%%%%%%%%%%%%%%%

\section{\sc Activities}
Rock Climbing - Yoga - VJing - Generative Arts - Photo - Biking

%%%%%%%%%%%% FIN %%%%%%%%%%%%%%%%

\end{resume}
\end{document}




